Polyester RNA-seq simulation study

### 2018-07-25 datasets/RNA-Seq/polyester-simulation.Rmd
Normalize counts before estimating polyester params; adjust beta coefficients

@@

  # DE simulation
  if(nDE > 0){
    wts <- log10(rowMeans(dat_alt)+1)
    DE <- sample(1:nrow(dat_alt), nDE, prob = wts)
    truth[DE] <- TRUE

    # randomly sample a log2FC from N(0,1) 
    log2FC[DE] <- rnorm(nDE, sd = 1)
    dat_alt[DE,] = create_read_numbers(mu[DE], paramPolyester$fit, p0[DE], 
                                  n=sampleSize*2, beta=cbind(log2FC[DE]), 
                                  mod=modPolyester)
  }

>>>>

# normalize
dds <- DESeqDataSetFromMatrix(countData = counts, 
                              colData = tibble(sample=colnames(counts)),
                              design = ~1)
dds <- estimateSizeFactors(dds)
counts <- counts(dds, normalize=TRUE)

@@

  # DE simulation
  if(nDE > 0){
    wts <- rowMeans(dat_alt)
    DE <- sample(1:nrow(dat_alt), nDE, prob = wts)
    truth[DE] <- TRUE

    # randomly sample a log2FC from N(0,1) 
    log2FC[DE] <- rnorm(nDE, sd = 1)
    dat_alt[DE,] = create_read_numbers(mu[DE], paramPolyester$fit, p0[DE], 
                                  n=sampleSize*2, beta=cbind(log2FC[DE]/2), 
                                  mod=modPolyester)
  }
